---
title: "NBA vs WNBA Metrics to Win Share"
author: "Stephen Monroe"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    theme: cerulean
  pdf_document:
    toc: true
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Packages Needed:** tidyverse

```{r,eval=TRUE,message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(readxl)
```

## Read Data In

```{r, echo=TRUE}
WNBA <- read_xlsx("Data/WNBA.xlsx")
NBA <- read_xlsx("Data/NBA.xlsx")
```

## Filter Data

```{r, echo=TRUE}
WNBA400 <- WNBA %>% 
  filter(MP >= 400)

NBA1000 <- NBA %>% 
  filter(MP >= 1000)
```


## NBA Regression

```{r, echo=FALSE}
NBA_Reg <- lm(WS~FG+FGA+FT+FTA+ORB+DRB+AST+STL+BLK+TOV+PF+PTS, data = NBA1000)
NBA_Scale <- NBA_Reg$coefficients/max(NBA_Reg$coefficients)
print(NBA_Scale)
```


## WNBA Regression

```{r,echo=FALSE}
WNBA_Reg <- lm(WS~FG+FGA+FT+FTA+ORB+DRB+AST+STL+BLK+TOV+PF+PTS, data = WNBA400)
WNBA_Scale <- WNBA_Reg$coefficients/max(WNBA_Reg$coefficients)
print(WNBA_Scale)
```

## Comparison

```{r, echo=FALSE}
Scaler <- WNBA_Scale/NBA_Scale
Scaler["PF"] <- abs(Scaler["PF"])
print(Scaler)
```

## Transform Current Coefficients

```{r, echo=FALSE}
Current <- c(.68, 26.77, 35.58, 26.32, 25.47, 42.74, 11.45, 29.70, 47.3, 38, 47.9, 18.8, 41.1)
names(Current) <- names(Scaler)
print(Current)
NewCoeff <- Scaler*Current
```

## Explanation

I took a regression of the stats included in PER against the wins score. I then took the coefficients and scaled them against the largest coefficient. I did this for the NBA and WNBA and then divided the WNBA by the NBA to create scalers for the WNBA against the known NBA PER. These then were scaled against the NBA PER coefficients. They are as follows:

```{r, echo=FALSE}
print(NewCoeff)
```